%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Sriranjan Sribhashyam} \\ \vspace{2pt}
    \href{mailto:ranjan31051997@gmail.com}{\underline{ranjan31051997@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/ranjansrinivas/}{\underline{linkedin/ranjansrinivas/}} $|$
    \href{https://github.com/rkaahean}{\underline{github.com/rkaahean}} $|$
    \href{https://ranjan.dev}{\underline{ranjan.dev}}

\end{center}

\section{Summary}
\small{
  I am a Data Engineer with 4 years of experience in building data-pipelines and analytics engineering using Python along with PostgreSQL and Snowflake.
  I am eligible for a \textbf{2 year visa}.
}

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages \& Frameworks}{: SQL, Python, Typescript, React, Next.js} \\
     \textbf{DevOps}{: CI/CD, Docker, Bash, Bazel, AWS SAA Certified (SAA\-C02)} \\
     \textbf{Data Management}{: (Py)Spark, ETL pipelines, dbt, Snowflake, FiveTran, PostgreSQL}
    }} \\
    \textbf{Data Science}{: pandas \& dask, PyTorch, matplotlib, seaborn, scikit-learn, OpenAI APIs}
 \end{itemize}



%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Engineer}{Feb 2021 -- Present}
      {ChipperCash}{Los Angeles, USA}
      \resumeItemListStart
        \resumeItem{Implemented an ELT batch pipeline for computing user risk rating using Python, pandas (dask) \& dbt models processing 10M+ rows in $\sim$2 hours and providing analysts with fresh data in Snowflake.}
        \resumeItem{Deployed ML models for inference as a microservice using Flask REST APIs, served over an event-driven architecture using RabbitMQ that handled \textgreater 1000 requests per minute.}
        \resumeItem{Optimized data loads from Snowflake using Apache Arrow, which sped up pipeline speeds by up-to 10x and decreased credit usage up-to 16x.}
        \resumeItem{Set up dbt for the analytics function which facilitated higher quality and faster data, for usage in upstream reporting tools like Looker \& Tableau.}
        % \resumeItem{Productionized a heuristic using XGBoost and a Python ETL data pipeline to predict user risk at onboarding, which helped cut referral fraud by 60\% and saved \$350k.}
        % \resumeItem{Created a ML model to forecast chargeback likelihood on card deposits, using transaction velocity and previous chargeback history as key features, effectively blocking $\sim$\$1.5M in high-risk deposits.}
        \resumeItem{Devised an automated Python data pipeline that declined up to 100 chargebacks per minute, thereby saving 200 hours of manual labor and preventing potential losses of $\sim$\$4M.}
        \resumeItem{Collaborated with PMs and Marketing to build a full-stack in-app messaging system, spanning React Native screens in the Mobile App,
        to backend REST APIs with TypeScript - thereby saving $\sim$\$80k/year by phasing out vendors.}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Data Engineer}{May 2020 -- Dec 2020}
      {Data Sleek}{Los Angeles, USA}
      \resumeItemListStart
        \resumeItem{Collaborated with 5+ clients to design, translate and implement business requirements into a technical spec.}
        \resumeItem{Delivered SQL stored procedures that perform analytical queries to detect and alert customers for changes in desired
metrics, saving up to 20\% of the base cost per item.}
        \resumeItem{Performed benchmark tests for several SingleStore configurations to determine optimal configuration for Time Series data, saving \$475/year while improving performance by 400\%.}
    \resumeItemListEnd

    \resumeSubheading
      {Software Engineer Intern}{May 2018 -- July 2018}
      {Samsung Research}{Bengaluru, India}
      \resumeItemListStart
        \resumeItem{Set up Open Network Automation Platform on a local server on top of Openstack, using docker containers, laying the
foundation for dynamically scalable ML applications based on resource requirements.}
        \resumeItem{Upgraded the ETL pipeline by deploying to Apache Kafka for streaming data to the microservice.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of California, Los Angeles}{Sep 2019 -- Dec 2020}
      {Masters of Science in Business Analytics}{Los Angeles, USA}
    \resumeSubheading
      {College of Engineering Guindy}{Jul 2015 -- May 2019}
      {B.S. Computer Science \& Engineering}{Chennai, India}
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Youtube Video Search} $|$ \emph{Python, OpenAI, Next.js, PostgreSQL, Typescript}}{\href{https://github.com/rkaahean/ask-ltt-wan}{\underline{github.com/youtube-search}}}
          \resumeItemListStart
            \resumeItem{Created a website that video-searched podcasts of a popular YouTube channel. Converted raw data into audio and transcribed it using whisper.cpp.}
            \resumeItem{Used pgvector to store and query embeddings, and generated context summary with gpt-3.5-turbo.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{MyAnimeList CLI} $|$ \emph{Rust}}{\href{https://github.com/rkaahean/mal-cli}{\underline{github.com/mal}}}
          \resumeItemListStart
            \resumeItem{Created an interactive CLI client in Rust to list anime based on a user's profile.}
            \resumeItem{Display detailed information regarding a show by parsing API.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
